### 2025-07-07 machine-learning.qmd
20250705 - tweaks
20250707 - citations

@@

@@

@@

@@

>>>>

The LASSO models were fit using the `glmnet` package [@R-glmnet; @Friedman2010_packages; @Tay2023_packages].

@@

The ridge regression models were fit using the `glmnet` package [@R-glmnet; @Friedman2010_packages; @Tay2023_packages].

@@

The elastic net models were fit using the `glmnet` package [@R-glmnet; @Friedman2010_packages; @Tay2023_packages].

@@

The random forest models were fit using the `ranger` package [@R-ranger; @Wright2017_packages].

@@

A summary of the accuracy of the machine learning models is in @tbl-machineLearningModelSummary.

### 2025-07-07 multiple-regression.qmd
20250707 - citations

@@

@@

@@

@@

@@

@@

betaRegression <- brm(
  formula = target_share ~ age + height + weight,
  data = newdata %>% filter(position %in% c("WR")),
  family = zero_one_inflated_beta(),
)
```

>>>>

We fit a linear regression model using the `lm()` function.

@@

We fit a logistic regression model using the `glm()` function and specifying `family = binomial()`.

@@

We fit an ordinal regression model using the `clm()` function of the `ordinal` package [@R-ordinal].

@@

We fit a Poisson regression model using the `glm()` function and specifying `family = poisson()`.

@@

We fit a negative binomial regression model using the `glm.nb()` function of the `MASS` package [@R-MASS].

@@

We fit a (Bayesian) zero-one-inflated beta regression model (to allow for zeros and ones) using the `brm()` function of the `brms` package [@R-brms] and specifying `family = zero_one_inflated_beta()`.

::: {#nte-bayesianBetaRegression .callout-note title="Bayesian beta regression"}
Note: the following code that runs the model takes a while.
:::

@@

betaRegression <- brms::brm(
  formula = target_share ~ age + height + weight,
  data = newdata %>% filter(position %in% c("WR")),
  family = zero_one_inflated_beta(),
)
```
